\documentclass[12pt,a4paper]{scrreprt}
\usepackage[utf8]{inputenc}
\usepackage[ngerman, english]{babel}


\author{Konrad Ritter}
\title{Funkspiel XXX Spieler 0}
\begin{document}
\maketitle
\section{Regeln}
\begin{itemize}
	\item RULE
\end{itemize}

\subsection{TaskID: 10}
\textbf{Aufgabenstellung}: Contact random and send the following information: \subsection{TaskID: 36}
\textbf{Aufgabenstellung}: This is a simulated emergency task. In all communication, make sure to always use the term 'simmulated emergency' to make sure this is not a real emergency. Do now start your stopwatch.Once it is started you need to declare the simmulated emergency on your communications channeland ask other players for emergency ressources.\subsection{TaskID: 31}
\textbf{Aufgabenstellung}: Contact random and send the following information: \subsection{TaskID: 23}
\textbf{Aufgabenstellung}: Contact random and send the following information: \subsection{TaskID: 30}
\textbf{Aufgabenstellung}: Contact {cp} and get the Information associated with the ID of this task.\subsection{TaskID: 38}
\textbf{Aufgabenstellung}: Contact random and send the following information: \subsection{TaskID: 14}
\textbf{Aufgabenstellung}: Contact random and send the following information: \subsection{TaskID: 52}
\textbf{Aufgabenstellung}: This is a simulated emergency task. In all communication, make sure to always use the term 'simmulated emergency' to make sure this is not a real emergency. Do now start your stopwatch.Once it is started you need to declare the simmulated emergency on your communications channeland ask other players for emergency ressources.\subsection{TaskID: 21}
\textbf{Aufgabenstellung}: Contact {cp} and get the Information associated with the ID of this task.\subsection{TaskID: 12}
\textbf{Aufgabenstellung}: Contact {cp} and get the Information associated with the ID of this task.\subsection{TaskID: 3}
\textbf{Aufgabenstellung}: Contact random and send the following information: \subsection{TaskID: 26}
\textbf{Aufgabenstellung}: Contact random and send the following information: \subsection{TaskID: 28}
\textbf{Aufgabenstellung}: This is a simulated emergency task. In all communication, make sure to always use the term 'simmulated emergency' to make sure this is not a real emergency. Do now start your stopwatch.Once it is started you need to declare the simmulated emergency on your communications channeland ask other players for emergency ressources.\subsection{TaskID: 37}
\textbf{Aufgabenstellung}: This is a simulated emergency task. In all communication, make sure to always use the term 'simmulated emergency' to make sure this is not a real emergency. Do now start your stopwatch.Once it is started you need to declare the simmulated emergency on your communications channeland ask other players for emergency ressources.\subsection{TaskID: 47}
\textbf{Aufgabenstellung}: Contact random and send the following information: \subsection{TaskID: 32}
\textbf{Aufgabenstellung}: This is a simulated emergency task. In all communication, make sure to always use the term 'simmulated emergency' to make sure this is not a real emergency. Do now start your stopwatch.Once it is started you need to declare the simmulated emergency on your communications channeland ask other players for emergency ressources.\subsection{TaskID: 53}
\textbf{Aufgabenstellung}: Contact {cp} and get the Information associated with the ID of this task.\subsection{TaskID: 40}
\textbf{Aufgabenstellung}: Contact {cp} and get the Information associated with the ID of this task.\subsection{TaskID: 29}
\textbf{Aufgabenstellung}: Contact {cp} and get the Information associated with the ID of this task.\subsection{TaskID: 5}
\textbf{Aufgabenstellung}: Contact {cp} and get the Information associated with the ID of this task.

\end{document}
