\documentclass[12pt,a4paper]{scrreprt}
\usepackage[utf8]{inputenc}
\usepackage[ngerman, english]{babel}


\author{Konrad Ritter}
\title{Funkspiel XXX Spieler 1}
\begin{document}
\maketitle
\section{Regeln}
\begin{itemize}
	\item RULE
\end{itemize}

\subsection{TaskID: 27}
\textbf{Aufgabenstellung}: Contact {cp} and get the Information associated with the ID of this task.\subsection{TaskID: 41}
\textbf{Aufgabenstellung}: Contact random and send the following information: \subsection{TaskID: 58}
\textbf{Aufgabenstellung}: Contact random and send the following information: \subsection{TaskID: 9}
\textbf{Aufgabenstellung}: Contact {cp} and get the Information associated with the ID of this task.\subsection{TaskID: 34}
\textbf{Aufgabenstellung}: Contact random and send the following information: \subsection{TaskID: 4}
\textbf{Aufgabenstellung}: Contact random and send the following information: \subsection{TaskID: 22}
\textbf{Aufgabenstellung}: Contact {cp} and get the Information associated with the ID of this task.\subsection{TaskID: 8}
\textbf{Aufgabenstellung}: Contact random and send the following information: \subsection{TaskID: 19}
\textbf{Aufgabenstellung}: Contact random and send the following information: \subsection{TaskID: 46}
\textbf{Aufgabenstellung}: This is a simulated emergency task. In all communication, make sure to always use the term 'simmulated emergency' to make sure this is not a real emergency. Do now start your stopwatch.Once it is started you need to declare the simmulated emergency on your communications channeland ask other players for emergency ressources.\subsection{TaskID: 24}
\textbf{Aufgabenstellung}: Contact {cp} and get the Information associated with the ID of this task.\subsection{TaskID: 50}
\textbf{Aufgabenstellung}: This is a simulated emergency task. In all communication, make sure to always use the term 'simmulated emergency' to make sure this is not a real emergency. Do now start your stopwatch.Once it is started you need to declare the simmulated emergency on your communications channeland ask other players for emergency ressources.\subsection{TaskID: 33}
\textbf{Aufgabenstellung}: This is a simulated emergency task. In all communication, make sure to always use the term 'simmulated emergency' to make sure this is not a real emergency. Do now start your stopwatch.Once it is started you need to declare the simmulated emergency on your communications channeland ask other players for emergency ressources.\subsection{TaskID: 0}
\textbf{Aufgabenstellung}: Contact {cp} and get the Information associated with the ID of this task.\subsection{TaskID: 44}
\textbf{Aufgabenstellung}: This is a simulated emergency task. In all communication, make sure to always use the term 'simmulated emergency' to make sure this is not a real emergency. Do now start your stopwatch.Once it is started you need to declare the simmulated emergency on your communications channeland ask other players for emergency ressources.\subsection{TaskID: 54}
\textbf{Aufgabenstellung}: Contact {cp} and get the Information associated with the ID of this task.\subsection{TaskID: 13}
\textbf{Aufgabenstellung}: Contact random and send the following information: \subsection{TaskID: 57}
\textbf{Aufgabenstellung}: This is a simulated emergency task. In all communication, make sure to always use the term 'simmulated emergency' to make sure this is not a real emergency. Do now start your stopwatch.Once it is started you need to declare the simmulated emergency on your communications channeland ask other players for emergency ressources.\subsection{TaskID: 18}
\textbf{Aufgabenstellung}: Contact {cp} and get the Information associated with the ID of this task.\subsection{TaskID: 17}
\textbf{Aufgabenstellung}: Contact {cp} and get the Information associated with the ID of this task.

\end{document}
