\documentclass[12pt,a4paper]{scrreprt}
\usepackage[utf8]{inputenc}
\usepackage[ngerman, english]{babel}


\author{Konrad Ritter}
\title{Funkspiel XXX Spieler 2}
\begin{document}
\maketitle
\section{Regeln}
\begin{itemize}
	\item RULE
\end{itemize}

\subsection{TaskID: 42}
\textbf{Aufgabenstellung}: Contact random and send the following information: \subsection{TaskID: 35}
\textbf{Aufgabenstellung}: Contact random and send the following information: \subsection{TaskID: 56}
\textbf{Aufgabenstellung}: Contact random and send the following information: \subsection{TaskID: 2}
\textbf{Aufgabenstellung}: Contact random and send the following information: \subsection{TaskID: 51}
\textbf{Aufgabenstellung}: This is a simulated emergency task. In all communication, make sure to always use the term 'simmulated emergency' to make sure this is not a real emergency. Do now start your stopwatch.Once it is started you need to declare the simmulated emergency on your communications channeland ask other players for emergency ressources.\subsection{TaskID: 39}
\textbf{Aufgabenstellung}: Contact {cp} and get the Information associated with the ID of this task.\subsection{TaskID: 15}
\textbf{Aufgabenstellung}: Contact random and send the following information: \subsection{TaskID: 59}
\textbf{Aufgabenstellung}: Contact random and send the following information: \subsection{TaskID: 20}
\textbf{Aufgabenstellung}: Contact {cp} and get the Information associated with the ID of this task.\subsection{TaskID: 11}
\textbf{Aufgabenstellung}: Contact random and send the following information: \subsection{TaskID: 49}
\textbf{Aufgabenstellung}: Contact {cp} and get the Information associated with the ID of this task.\subsection{TaskID: 25}
\textbf{Aufgabenstellung}: This is a simulated emergency task. In all communication, make sure to always use the term 'simmulated emergency' to make sure this is not a real emergency. Do now start your stopwatch.Once it is started you need to declare the simmulated emergency on your communications channeland ask other players for emergency ressources.\subsection{TaskID: 48}
\textbf{Aufgabenstellung}: This is a simulated emergency task. In all communication, make sure to always use the term 'simmulated emergency' to make sure this is not a real emergency. Do now start your stopwatch.Once it is started you need to declare the simmulated emergency on your communications channeland ask other players for emergency ressources.\subsection{TaskID: 6}
\textbf{Aufgabenstellung}: This is a simulated emergency task. In all communication, make sure to always use the term 'simmulated emergency' to make sure this is not a real emergency. Do now start your stopwatch.Once it is started you need to declare the simmulated emergency on your communications channeland ask other players for emergency ressources.\subsection{TaskID: 1}
\textbf{Aufgabenstellung}: This is a simulated emergency task. In all communication, make sure to always use the term 'simmulated emergency' to make sure this is not a real emergency. Do now start your stopwatch.Once it is started you need to declare the simmulated emergency on your communications channeland ask other players for emergency ressources.\subsection{TaskID: 16}
\textbf{Aufgabenstellung}: This is a simulated emergency task. In all communication, make sure to always use the term 'simmulated emergency' to make sure this is not a real emergency. Do now start your stopwatch.Once it is started you need to declare the simmulated emergency on your communications channeland ask other players for emergency ressources.\subsection{TaskID: 45}
\textbf{Aufgabenstellung}: Contact {cp} and get the Information associated with the ID of this task.\subsection{TaskID: 7}
\textbf{Aufgabenstellung}: Contact {cp} and get the Information associated with the ID of this task.\subsection{TaskID: 43}
\textbf{Aufgabenstellung}: Contact {cp} and get the Information associated with the ID of this task.\subsection{TaskID: 55}
\textbf{Aufgabenstellung}: Contact random and send the following information: 

\end{document}
